---
output: bookdown::gitbook
---
# Activity 3 - Sampling Distributions Related to the Normal Model

## Context of Data

At-term newborns in Canada vary in weight according to an approximate **Normal model**, with the following parameters:
- Mean: 3500 grams
- Standard Deviation: 500 grams

The objective of this activity is to explore the sampling distributions of sample means and understand how they relate to the normal distribution.

---

## R Setup

To set up and use R for this activity, follow the general instructions provided here:  
[**How to Access and Use R for Data Analysis Activities**](#how-to-set-up-r-for-data-analysis-activities).

Once you’ve set up your project and loaded the provided files, proceed with the activity-specific instructions below.

---

## Activity Instructions

1. Open the R script [`Newborn_Weights.R`](https://raw.githubusercontent.com/aslemand/Data-Analysis-Activities/main/data/Activity_3/Newborn_Weights.R) and start running the provided code.
2. Modify the R code as follows:
   - **Line 7**: Insert a unique seed number.
   ```{r, eval = FALSE}
   # Enter your seed number in line 8.
   set.seed( )
   ```
   - **Line 39**: Add your last name to the title of the plot.
   ```{r, eval = FALSE}
   # Make a change to line 40. Include your last name in the main (title) argument.
   hist(Xbar, 
      main = "Histogram of Sample Means \n Conducted by You", 
      xlab = "Xbar: Sample Means for Total Weights (in grams) of New Borns", 
      col = "lavender")
   ```
3. Simulate 100 samples of size \(n = 30\) from the population distribution of newborn weights. Store the means in a variable named `Xbar`.
4. Construct a frequency histogram of the sampling distribution of sample means. Obtain summary statistics and interpret:
   - Shape
   - Center
   - Spread
5. Experiment with other sample sizes (\(n = 2, 5, 15, 30, 100, 300\)) using different replication numbers (\(n = 1000\)):
   - Plot the sampling distributions of sample means for these sample sizes.
   - Identify which sample size gives the smallest **Standard Error**.

---

## Related Questions

After completing the activity, answer the following questions:

1. **Sampling Distribution Analysis**:
   - Using the boxplot and Normal QQ plot, describe the sampling distribution of your sampled data. Justify your answer with both visualizations.

2. **IQR Extrapolation**:
   - Refer to the summary statistics. Write a sentence that extrapolates the **IQR** for this sample into a statement about the population. Ensure your wording is precise.

3. **Sampling Distribution of Means**:
   - For \(n = 30\), describe the sampling distribution of sample means (shape, center, and spread). Use summary statistics and histogram to support your analysis.

4. **Effect of Sample Size**:
   - Compare sampling distributions for different sample sizes (\(n = 2, 5, 15, 30, 100, 300\)).
   - Identify which sample size gives the smallest **Standard Error** and explain why.

---

## Submission Instructions

- Save the histogram of the sampling distribution of sample means for newborn weights (\(n = 30\)) as a `.doc`, `.pdf`, `.jpeg`, or `.png` file.
- Provide your file to your instructor or teaching assistant for feedback or assessment.
