---
output: bookdown::gitbook
---
# Activity 6 - Introduction to Hypothesis Testing and Concepts

## Tutorial Objective

The objective of this week's module is to equip you with the following:

- Use R/RStudio on a desktop/laptop to carry out hypothesis testing and to estimate error probability via simulation.
- Employ hypothesis testing for:
    - **One Proportion**
    - **One Mean**  
        - Sigma known, Normal population:  
            - Large sample  
            - Small sample  
        - Sigma unknown, estimate sigma (replace with sample standard deviation):  
            - Large sample, CLT applies  
            - Small sample, assess (or know) whether the random sample comes from a Normal population.  
    - **One Variance**  
        - Independent, (small or large) random sample.  



---

## Pre-Task Tutorial Activity

### Context of the Problem for Carrying Out Simulations

Suppose **STA123 course grades** are Normally distributed with a mean of **70** and a standard deviation of **5**.  

Estimate the error probability in a t-test of \( H_0: \mu = 70 \) versus \( H_a: \mu > 70 \), when the underlying population is Normal with \( \mu = 70 \) and \( \sigma = 5 \). Take a random sample of \( n = 25 \) and test at \( \alpha = 0.05 \).

Using the STA123 course grades example, we can conduct an experiment using the following steps:
1. Generate a set of **10,000** STA123 course grades data with 25 students from the population.
2. For each of the generated random samples, conduct a t-test.
3. Store the observed t-test statistics and the p-values in a matrix.
4. Count the number of p-values that are \( \leq 0.05 \) (\(\alpha\)-level) to estimate the probability of error.

---

## Steps to Complete the Activity

1. Download the following file to your computer:
   - [R Script: Hypothesis Testing-Error Probability-Simulation.R](https://raw.githubusercontent.com/aslemand/Data-Analysis-Activities/main/data/Activity_6/Hypothesis-Testing-Error-Probability-Simulation.R)

2. Follow the instructions provided on the **How to Access and Use R for Data Analysis Activities** page to set up your R environment:  
   [**How to Access and Use R for Data Analysis Activities**](#how-to-set-up-r-for-data-analysis-activities).

3. Once you’ve set up your project folder and uploaded the file, proceed with the steps below:
   - Open the R script `Hypothesis Testing-Error Probability-Simulation.R` and start running the provided code.

4. There are two required R code modifications:
   - **Line 10**: You need to input a seed number. You are provided with a unique seed number that you can retrieve from Quercus in your Grade page (see [Seed Number](#)). Find your seed number and put it into line 10 and run the line of code in R.
   ```{r, eval=FALSE}
   # R code modification #1: 
   # Enter your seed number inside the function set.seed( ) 
   # set.seed() function in R will create reproducible results.
   set.seed()
   ```
   - **Line 75**: You need to insert your last name in the title of the plot. Make the change to this line and upload your plot using this assignment page.
   ```{r, eval=FALSE}
   # R code modification #2: 
   # Make a change to the main (title) of the plot by adding your last name to it.
   library(ggplot2)
   hist.plot = ggplot(data = HT.Array) 
   hist.plot = hist.plot + geom_histogram(aes(x = t.Stat,
                                              y = after_stat(count / sum(count)),
                                              fill = P.value <= 0.05), 
                                          binwidth = 0.5, 
                                          color = 'black')
   hist.plot = hist.plot + scale_fill_manual(values=c("lightgrey", "darkorange"), 
                                             name="P.values <= 0.05",
                                             labels=c("No", "Yes"))
   hist.plot = hist.plot + labs(x = "t Statistics", 
                                y = "Proportion")
   hist.plot = hist.plot + ggtitle('Simulated t Statistics Conducted by You')
   hist.plot + theme_bw() + theme(plot.title=element_text(hjust=0.5))
   ```
  
---

## Related Questions

Based on your R analysis (using your R outputs), answer the following related questions:

1. Briefly describe the result of your simulation. What do you observe?

---

## Required R Output for Submission

Using this assignment page, upload your histogram of t-statistics based on your simulated data. The accepted file formats for Quercus submission are `.doc`, `.pdf`, `.jpeg`, or `.png` files.
